\textsf{Are frontier models superhuman chemists?}

### 2024-03-14 src/tex/ms.tex
update abstract

    % Two or three sentences explaining what the main result reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge
    We curated more than 6000 question answer pairs about a wide array of subfields, evaluated leading models such as GPT-4, and found that the best models, on average, outperform the best human chemists in our study. 
    The models, however, struggle with some chemical reasoning tasks that are easy for human experts and give overconfident misleading predictions, e.g. about the safety profile of chemicals.

    % One or two sentences to put the results into a more general context.

\end{abstract}

>>>>

    We curated more than 6000 question answer pairs about a wide array of subfields, evaluated leading models such as GPT-4, and found that the best models, on average, outperform the best human chemists in our study. 
    The models, however, struggle with some chemical reasoning tasks that are easy for human experts and give overconfident misleading predictions, e.g. about the safety profile of chemicals.

    Our results demonstrate that while frontier models show outstanding performance on chemical tasks, additional research is required to ensure useful and safe chemical language models. 
    The findings also suggest that chemistry curricula might need to adapt and that continued development of evaluation frameworks is critical for systematic improvement of LLMs.
\end{abstract}
